\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-24 draft.tex
Typos in 4.1

%-----------------------------------------------------------------------------
\subsubsection{Handling output inside the loop body} 
%-----------------------------------------------------------------------------

@@

\subsubsection{Benchmark collection} In order to properly evaluate the performance of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''. Since there is an upper bound on the number of results returned from the search engine, we add different search filters in order to get more data. We tried all $12$ combinations of six filters on code length $\{<50$, $ 50\sim 250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim 1250\}$
and two filters for data sources $\{\url{github.com}, \url{bitbuckect.com}\}$. In total, we get $11346$ Java programs. We exclude cases that are not Hadoop MapReduce reducer programs (those do not import the Hadoop library, do not extend or implement the reducer interface) and obtain $1273$ examples. We further remove those that cannot be compiled, those that are identical to each other, or those with non-numerical data types (e.g, string) and obtained $118$ reducers as the final benchmarks. Figure~\ref{fig:benchmark} contains the details of extracted reducer functions.

\subsubsection{Results} J-ReCoVer successfully handled $115$ cases ($97.4\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
On average, $72\%$ of the execution time is in compiling JAVA source code to bytecode, which is the input of the Soot tool. Another $27\%$ of the execution time is in the Propossesor, in which Soot is used to transform JAVA bytecode to Jimple and perform the program transformations. The time spent in Solver is quite limited ($<1\%$), since the real-world integer reducer programs are usually not that big.

>>>>

%-----------------------------------------------------------------------------
\paragraph*{Handling output inside the loop body} 
%-----------------------------------------------------------------------------

@@

\paragraph*{Benchmark collection} In order to properly evaluate the performance of J-ReCoVer, We use the search engine \emph{searchcode.com} to collect java programs containing the key strings ``public void reduce'' or ``protected void reduce''. Since there is an upper bound on the number of results returned from the search engine, we add different search filters in order to get more data. We tried all $12$ combinations of six filters on code length $\{<50$, $ 50\sim 250$, $250\sim 450$, $450\sim 650$, $650\sim 850$, $850\sim 1050$, $1050\sim 1250\}$
and two filters for data sources $\{\url{github.com}, \url{bitbuckect.com}\}$. In total, we get $11346$ Java programs. We exclude cases that are not Hadoop MapReduce reducer programs (those do not import the Hadoop library, do not extend or implement the reducer interface) and obtain $1273$ examples. We further remove those that cannot be compiled, those that are identical to each other, or those with non-numerical data types (e.g, string) and obtained $118$ reducers as the final benchmarks. Figure~\ref{fig:benchmark} contains the details of extracted reducer functions.

\paragraph*{Results} J-ReCoVer successfully handled $115$ cases ($97.4\%$). The analysis time ranges between $9.8$ to $8.6$ seconds. 
On average, $72\%$ of the execution time is in compiling JAVA source code to bytecode, which is the input of the Soot tool. Another $27\%$ of the execution time is in the Propossesor, in which Soot is used to transform JAVA bytecode to Jimple and perform the program transformations. The time spent in Solver is quite limited ($<1\%$), since the real-world integer reducer programs are usually not that big.
